---
title: "Introducing CPS Enrollment Datasets"
author: "Charlotte Mack"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# CPSenrollpack

This repository contains enrollment data that were extracted from Chicago Public Schools (CPS) public records. The prepared data are available at this repository in Rds and csv formats; at present there are only high school data, with elementary school data forthcoming. The sets span the school years from 2006--2007 through 2018--2019, and will be periodically updated.

## Installation

You can install the released version of CPSenrollpack from [github](https://github.com/cymack/CPSenrollpack). If you do not have the devtools package, then first install it from [CRAN](https://cran.r-project.org/):
``` r
install.packages(devtools)
```

Then use the devtools install command as follows:

``` r
install_github("cymack/CPSenrollpack")
```

How to access the data.

```{r example}
## basic example code
```
